site_map

### 2020-09-21 site_map.Rmd
update

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
   geom_polygon(aes(group = group),fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE)+
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 2) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "red", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub, aes(x = lon, y = lat, label = site),
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2,
                     segment.alpha = 0.4, force = 0.1, font = "Palatino") +
  xlab("") + ylab("") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 16.5, y = -31.5,
             size =5, angle = 0, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_y_continuous(breaks = seq(-34, -28, by = 2),
                     labels  = c("34°S","32°S","30°S","28°S")) +
  scale_x_continuous(breaks = seq(16, 20, by = 2),
                      labels = c("16°E", "18°E", "20°E")) +
 coord_fixed(ratio = 1, xlim = c(15.4, 20), ylim = c(-34.4,-27),
    expand = TRUE) +
  theme(axis.text = element_text(size = rel(1.2), colour = "black", family = "Palatino"),
        axis.text.x = element_text(vjust = 1, family = "Palatino", size = 22),
        axis.text.y = element_text(hjust = 1, family = "Palatino", size = 22),
        axis.title.x = element_text(vjust = 0, family = "Palatino"),
        axis.title.y = element_text(angle = 90, vjust = 0.3, family = "Palatino"),
        axis.ticks = element_line(colour = "black"),
        axis.ticks.length = unit(0.4, "cm"),
        #axis.ticks.length = unit(0.15, "cm"),
        axis.ticks.margin = unit(0.1, "cm"),
        panel.background = element_rect(fill = "white", colour = "black", size = 0.5),
        #panel.border = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        #(colour =" black"),
        panel.grid.major.x = element_blank(),
        #panel.grid.major.y = element_line(linetype = "dotted", size = 0.2, colour = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.margin = unit(0.25, "lines"),
        strip.text = element_text(size = rel(1.0), family = "Palatino"),
        strip.background = element_rect(fill = "white", colour = NA),
        strip.text.x = element_text(),
        strip.text.y = element_text(angle = -90),        
        plot.background = element_rect(colour = "white"),
        plot.title = element_text(size = rel(1.2), vjust = 1),
        plot.margin = unit(c(1, 1, 0.5, 0.5), "lines"))

@@

africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) + 
  theme_bw() + 
  coord_equal() + 
  geom_polygon(aes(group = group), colour = "black", fill = "grey80") + 
  geom_polygon(data = sa_provinces_new, (aes(group = group))) +
  annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) + 
  theme(panel.border = element_rect(colour = "black", size = 0.4), 
        plot.background = element_blank(), 
        axis.ticks = element_blank(), 
        axis.text = element_blank(), 
        axis.title = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator") 
africa_map

sa_4 <- site_map +
annotation_custom(grob = ggplotGrob(africa_map),
xmin = 20.9, xmax = 26.9,
ymin = -30, ymax = -24)
sa_4
```

>>>>

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
   geom_polygon(aes(group = group),fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE)+
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 2) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "red", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub, aes(x = lon, y = lat, label = site),
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2,
                     segment.alpha = 0.4, force = 0.1, font = "Palatino") +
  xlab("") + ylab("") +
    # annotate("text", label = "ATLANTIC\nOCEAN", x = 16.5, y = -31.5,
    #          size =5, angle = 0, colour = "black") +
  annotate("text", label = "Cape Columbine", x = 16.0, y = -30.5,
             size =5, angle = 45, colour = "black")+
  annotate("text", label = "Cape Peninsula", x = 16.5, y = -33.9,
             size =5, angle = 45, colour = "black")+
  guides(fill = guide_colourbar()) +
  scale_y_continuous(breaks = seq(-34, -28, by = 2),
                     labels  = c("34°S","32°S","30°S","28°S")) +
  scale_x_continuous(breaks = seq(16, 20, by = 2),
                      labels = c("16°E", "18°E", "20°E")) +
 coord_fixed(ratio = 1, xlim = c(15.4, 20), ylim = c(-34.4,-27),
    expand = TRUE) +
  theme(axis.text = element_text(size = rel(1.2), colour = "black", family = "Palatino"),
        axis.text.x = element_text(vjust = 1, family = "Palatino", size = 22),
        axis.text.y = element_text(hjust = 1, family = "Palatino", size = 22),
        axis.title.x = element_text(vjust = 0, family = "Palatino"),
        axis.title.y = element_text(angle = 90, vjust = 0.3, family = "Palatino"),
        axis.ticks = element_line(colour = "black"),
        axis.ticks.length = unit(0.4, "cm"),
        #axis.ticks.length = unit(0.15, "cm"),
        axis.ticks.margin = unit(0.1, "cm"),
        panel.background = element_rect(fill = "white", colour = "black", size = 0.5),
        #panel.border = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        #(colour =" black"),
        panel.grid.major.x = element_blank(),
        #panel.grid.major.y = element_line(linetype = "dotted", size = 0.2, colour = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.margin = unit(0.25, "lines"),
        strip.text = element_text(size = rel(1.0), family = "Palatino"),
        strip.background = element_rect(fill = "white", colour = NA),
        strip.text.x = element_text(),
        strip.text.y = element_text(angle = -90),        
        plot.background = element_rect(colour = "white"),
        plot.title = element_text(size = rel(1.2), vjust = 1),
        plot.margin = unit(c(1, 1, 0.5, 0.5), "lines"))

@@

africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) +
  theme_bw() +
  coord_equal() +
  geom_polygon(aes(group = group), colour = "black", fill = "grey80") +
  geom_rect(data=africa_coast, aes(xmin=15.0, xmax=21.0, ymin=-34.4, ymax=-29.5),  colour = "red", fill = NA, size = 0.35) +
  geom_polygon(data = sa_provinces_new, (aes(group = group))) +
  #annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) +
  theme(panel.border = element_rect(colour = "black", size = 0.4),
        plot.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator")
africa_map

sa_4 <- site_map +
annotation_custom(grob = ggplotGrob(africa_map),
xmin = 17, xmax = 21.5,
ymin = -28.8, ymax = -26.6)
sa_4
```
